### 2018-04-30 paper/global-overlay-design.tex
Replaces some of Adrien's PORs with \acp{SPOR}

To reach this goal, we employ Random Peer Sampling (RPS) \cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
Essentially, each node maintains a \emph{view} containing \viewsize other devices' descriptors. 
By periodically exchanging random descriptors with a carefully selected node from its view, RPS allows devices to always have a fairly random sample of the nodes in the system inside their view.
Due to the RPS's eviction policy, stale descriptors are removed quickly: each device thus knows a random sample of \viewsize connected nodes.
An RPS descriptor for device $d$ is constituted of the following information:
\begin{itemize}
  \item Its address: $@_d$;
  \item Its public key: \(\pk_d\);
  \item Its probability of being online in the near future, as provided by the Squad Overlay: $p_d=P\left[d \in O_{t+1} | S_t\right]$.
\end{itemize}

>>>>

To reach this goal \david{which one?}, we employ Random Peer Sampling (RPS) \cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
Essentially, each node maintains a \emph{view} containing \viewsize other devices' descriptors. 
By periodically exchanging random descriptors with a carefully selected node from its view, RPS allows devices to always have a fairly random sample of the nodes in the system inside their view.
Due to the RPS's eviction policy, stale descriptors are removed quickly: each device thus knows a random sample of \viewsize connected nodes.
An RPS descriptor for device $d$ is constituted of the following information:
\begin{itemize}
  \item Its address: $@_d$;
  \item Its public key: \(\pk_d\);
  \item Its probability of being online in the near future, as provided by the Squad Overlay: $p_d=P\left[d \in O_{t+1} | S_t\right]$.
\end{itemize}

### 2018-04-30 paper/squad-overlay-design.tex

\subsection{The E-Squad Overlay} 
\label{sec:squad_overlay}

@@

In this section, we only take interest in one user (called Alice) and her squad.

@@

\paragraph*{Other uses of the Squad Overlay} In addition to user's behavior, devices use th \squad Overlay for several purposes. Firstly, they share files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly. 
Secondly, each device is also informed of its user's ongoing file transfers (which serves the next purpose).

\david{the following paragraph is not clear at all }
\name knows two message types (as will be covered in~\ref{sec:file_exchange}): file chunk, and acknowledgment.
Alice typically wants to receive a file on one particular device; respectively, only one of her devices is interested in acknowledging reception of the file chunks it is sending. \david{what is the relationship with \squad Overlay?}
However, \name allows all squad members to receive messages destined to Alice.
Thus, the third complementary purpose of the Squad Overlay is to relay messages among the squad: when a message is not destined to the device that received it, the receiver forwards the message to its final destination.
\david{and then?}

>>>>

\subsection{The \squad Overlay} 
\label{sec:squad_overlay}

@@

In this section, we only take interest in one user (called Alice) and her \squad.

@@

\paragraph*{Other uses of the \squad Overlay} In addition to user's behavior, devices use th \squad Overlay for several purposes. Firstly, they share files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly. 
Secondly, each device is also informed of its user's ongoing file transfers (which serves the next purpose).
Finally, because devices can receive messages on behalf of their fellow squad members to ensure reception despite the proper recipient being offline, 
one's devices can forward messages among the \squad.

% \david{the following paragraph is not clear at all }
% \name knows two message types (as will be covered in~\ref{sec:file_exchange}): file chunk, and acknowledgment.
% Alice typically wants to receive a file on one particular device; respectively, only one of her devices is interested in acknowledging reception of the file chunks it is sending. \david{what is the relationship with \squad Overlay?}
% However, \name allows all \squad members to receive messages destined to Alice.
% Thus, the third complementary purpose of the \Squad Overlay is to relay messages among the squad: when a message is not destined to the device that received it, the receiver forwards the message to its final destination.
% \david{and then?}
